---
title: "IMDB database"
author: "Xing Yang"
date: "2017/12/4"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(tidyverse)
library(rvest)
library(stringr)
library(RSQLite)
library(dplyr)
library(ggplot2)
library(h2o)
library(caret)
```

# Collection data

I uesd css selector to collector data from IMDB, the first thing what I did was just collect one page infomation which contain name, year, director, stars, genre, certificate, gross, rating and introduction. In there, for easy to analysis, I just extracted one genre, one director and two stars from each movie.

```{r}
get_onpage <- function(genre, page){
  url <- 'http://www.imdb.com/search/title?genres=%s&explore=genres&sort=boxoffice_gross_us,desc&page=%s&re_=adv_nxt'
  page <- as.character(page)
  url <- sprintf(url, URLencode(genre), URLencode(page))
  imdbsr <- read_html(url)
  basic <- imdbsr %>%
  html_nodes(".mode-advanced") %>%
    purrr::map(function(item) {
      tibble(
        name = item %>%
          html_node(".lister-item-header a") %>%  
          html_text(trim=T),
        year = item %>%
          html_node(".text-muted.unbold") %>%  
          html_text(trim=T) %>%
          str_extract("[0-9]{4}") %>%
          as.numeric(),
        certificate = item %>%
          html_node(".certificate") %>%  
          html_text(trim=T),
        runtime = item %>%
          html_node(".runtime") %>%  
          html_text(trim=T) %>%
          str_extract("[0-9]+") %>%
          as.numeric(),
        genre = item %>% # just got the first genre
          html_node(".genre") %>%  
          html_text(trim=T) %>%
          str_replace_all(",\\s[A-Z]{1}[a-z]+", ""),
        director = item %>% # also, the first director
          html_node(".text-muted~ .text-muted+ p , .ratings-bar~ .text-muted+ p") %>%  
          html_text() %>%
          str_extract("Director[\\S]*:\n.+\n") %>%
          unlist() %>%
          str_replace_all(c(
            "Director[\\S]*:" = "",
            "\n" = "",
            "\\s{2}" = "",
            "\\|" = "",
            "," = "")),
        stars = item %>%
          html_node(".text-muted~ .text-muted+ p , .ratings-bar~ .text-muted+ p") %>%  
          html_text() %>%
          str_extract("((Stars:\n.+\n.+\n)|(Star:\n.+\n))") %>%
          str_replace_all(c(
            'Star[\\S]*:' = "",
            '\n' = "")),
        rating = item %>%
          html_node("strong") %>%  
          html_text(trim=T) %>%
          as.numeric(),
        gross = item %>%
          html_node(".sort-num_votes-visible") %>%
          html_text() %>%
          str_extract("Gross:\n.+\n") %>%
          str_extract("[0-9]+.[0-9]") %>%
          as.numeric(),
        metascore = item %>%
          html_node(".ratings-metascore") %>%  
          html_text(trim=T) %>%
          str_extract("[0-9]+") %>%
          as.numeric(),
        votes = item %>%
          html_node(".sort-num_votes-visible") %>%
          html_text() %>%
          str_extract("Votes:\n.+\n") %>%
          str_replace_all(c(
            "Votes:" = "",
            "\n" = "",
            "," = "",
            "\\s*" = "")) %>%
          as.numeric(),
        intro = item %>%
          html_node(".text-muted+ .text-muted , .ratings-bar+ .text-muted") %>%  
          html_text(trim=T)
          )
    }) %>% bind_rows()
   return(basic)
}
```

Then I writed another function to get mutliple pages.

```{r}
get_mtp_page_sleep <- function(genre, startpage, endpage){
  a = matrix(ncol = 12, nrow = 0)
for (i in startpage : endpage){
  onepage = get_onpage(genre, page = i)
  a = rbind(a, onepage)
  Sys.sleep(1)
}
  outcome = as.data.frame(a, stringsAsFactors = FALSE)
  return(outcome)
}

get_mtp_page_sleep(genre = "action", startpage = 3, endpage = 4)
```

So, I got the funtion to extract data from IMDB, then I search movies by genre and make sure the gross woube be lager the 0. Since the different genre has different number of moives, so I searched the different number of pages for differnet genre and the final page should be that gross is equla to zero. 

```{r}
#diferent pages for different genre
page_65 <- c("comedy", "drama")
page_40 <- c("action", "crime", "romance", "thriller")
page_25 <- c("adventure")
page_20 <- c("fantasy", "sci_fi", "horror", "family", "documentary", "mystery")
page_15 <- c("music", "biography")
page_10 <- c("history", "war", "animation", "sport")
page_4 <- c("western")

movie_65 <- matrix(ncol = 12, nrow = 0)
for(i in 1:length(page_65)){
  a <- get_mtp_page_sleep(genre = page_65[i], startpage = 1, endpage = 65)
  movie_65 <- rbind(movie_65, a)
}

movie_40 <- matrix(ncol = 12, nrow = 0)
for(i in 1:length(page_40)){
  a <- get_mtp_page_sleep(genre = page_40[i], startpage = 1, endpage = 40)
  movie_40 <- rbind(movie_40, a)
}

movie_25 <- matrix(ncol = 12, nrow = 0)
for(i in 1:length(page_25)){
  a <- get_mtp_page_sleep(genre = page_25[i], startpage = 1, endpage = 25)
  movie_25 <- rbind(movie_25, a)
}

movie_20 <- matrix(ncol = 12, nrow = 0)
for(i in 1:length(page_20)){
  a <- get_mtp_page_sleep(genre = page_20[i], startpage = 1, endpage = 20)
  movie_20 <- rbind(movie_20, a)
}

movie_15 <- matrix(ncol = 12, nrow = 0)
for(i in 1:length(page_15)){
  a <- get_mtp_page_sleep(genre = page_15[i], startpage = 1, endpage = 15)
  movie_15 <- rbind(movie_15, a)
}

movie_10 <- matrix(ncol = 12, nrow = 0)
for(i in 1:length(page_10)){
  a <- get_mtp_page_sleep(genre = page_10[i], startpage = 1, endpage = 10)
  movie_10 <- rbind(movie_10, a)
}

movie_4 <- matrix(ncol = 12, nrow = 0)
for(i in 1:length(page_4)){
  a <- get_mtp_page_sleep(genre = page_4[i], startpage = 1, endpage = 4)
  movie_4 <- rbind(movie_4, a)
}

#combinded these dataframe together and delete the same rows. 
movie_duplicated <- as.data.frame(rbind(movie_65, movie_40, movie_4, movie_25, movie_20, movie_15, movie_10))
movie_stars <- movie_duplicated[!duplicated(movie_duplicated[c("intro")]), ]

#separet star into star1 and star2
movies <- movie_stars %>%
  filter(gross > 1) %>%
  separate(stars, into = c("star1", "star2", "delete"), sep = ",\\s") %>%
  select(-delete)

#clean data 
movies$genre <- str_replace_all(movies$genre, c("-Fi" = "", "-Noir" = ""))
movies$certificate[which(is.na(movies$certificate))] <- "Unrated"
movies$certificate[which(movies$certificate == "Not Rated")] <- "Unrated"
movies$certificate[which(movies$certificate == "PG")] <- "M/PG"
movies$certificate[which(movies$certificate == "M")] <- "M/PG"
movies$certificate[which(movies$certificate == "Approved")] <- "Passed"
head(movies)

#save data 
write.csv(movies, file = "/Users/xingyang/Desktop/5020/movies.csv")
```

# Storing data

I stored data into NoSQL, and the primary key is name, year, director. 

```{r}
#save data into database
db <- dbConnect(SQLite(),dbname="project.sqlite")
dbGetQuery(db, "CREATE TABLE movies(
           name TEXT,
           year INTEGER,
           certificate TEXT,
           runtime INTEGER,
           genre TEXT,
           director TEXT,
           star1 TEXT,
           star2 TEXT,
           rating NUMERIC,
           gross NUMERIC,
           metascore INTEGER,
           votes INTEGER,
           intro TEXT,
           PRIMARY KEY (name, year, director)
           )")
dbWriteTable(db, "movies", movies, append=TRUE, row.names=FALSE)
#dbRemoveTable(db, "movies")
```

# Retrieve data 

In there, I wrote some functions to retrieve data use SQL expression, I also used dplyr to retrieve data. 

```{r}
#Q1: which movie does have the highest boxffice
query <- "SELECT name, year, director, gross, rating, star1, star2
          FROM movies
          ORDER BY gross DESC
          LIMIT 3;"
dbGetQuery(db, query)

average_best <- function(type, best){
  dbGetQuery(db, query <- str_c("SELECT ", type, ", AVG(",best,") FROM movies GROUP BY ", type, " ORDER BY AVG(",best,") DESC LIMIT 1"))}

#Q2: Who is the highest average box office director?
average_best('director', 'gross')

#Q3: Who is the highest average rating star?
average_best('star1', 'rating')
average_best('star2', 'rating')

#Q4: Which genre of movie did get the higest average runtime?
average_best('genre', 'runtime')

#Q5: Which type of certificate did has the higest average vote?
average_best('certificate', 'votes')

#Q6: Which movies did get the rating larger than 9
movies %>%
  filter(rating > 9) %>%
  select(name, year, rating, gross, intro)

#select movie function
movie_type_best <- function(type, best){
  dbGetQuery(db, query <- str_c("SELECT name, ", type, ", MAX(",best,") FROM movies GROUP BY ", type, " ORDER BY MAX(",best,") DESC LIMIT 10"))}

#Q7: Which movie is the highest box office for each genre?
movie_type_best(type = 'genre', best = 'gross')

#Q8: Which movie is the highest runtime for each certificate? 
movie_type_best(type = 'certificate', best = 'runtime')

#Q9: Which movie is the highest rating for each star? 
movie_type_best(type = 'star1', best = 'rating')
movie_type_best(type = 'star2', best = 'rating')

#Q10: Which movie is the highest vote for each year?
movie_type_best(type = 'year', best = 'rating')

type_best <- function(type, best){
  dbGetQuery(db, query <- str_c("SELECT ", type, ", MAX(",best,") FROM movies GROUP BY ", type, " ORDER BY MAX(",best,") DESC LIMIT 1"))}

#Q11: Which year does have the highest box office?
type_best(type = 'year', best = 'gross')

#Q12: Which genre does get the highest votes?
type_best(type = 'genre', best = 'votes')

#Q13: Which certificate does have the most number of movies?
movies %>%
  count(certificate) %>%
  arrange(desc(n)) %>%
  head(1)
```

# Visualiztion

```{r}
#the total gross trend from 1990 
movies %>% 
  group_by(year) %>% 
  summarise(total_gross = sum(gross)) %>%
  filter(year >= 1990, total_gross > 1000) %>%
  ggplot(aes(year, total_gross)) +
    geom_point() +
    geom_smooth(method = "loess", se = F) +
    ggtitle("The Trend of Total Gross")

#the total gross over 1000 trend from 1990 for each genre
movies %>% 
  group_by(year, genre) %>% 
  summarise(total_gross = sum(gross)) %>%
  filter(year >= 1990, total_gross > 500) %>%
  ggplot(aes(year, total_gross, color = genre)) +
    geom_line() +
    ggtitle("The Gross Trend for Each Genre")

#the number of movie for each genre
ggplot(movies, aes(genre, fill = genre)) + 
  geom_bar() +
  theme_bw() +
  ggtitle("The Number of Movies for Each Genre")

#the number of movie for each certificate
ggplot(movies %>% filter(year == 2010), aes(certificate, fill = certificate)) + 
  geom_bar() +
  theme_bw() +
  ggtitle("The Number of Movies for Each Certificate")

#the relationship between rating and gross from 1990
ggplot(data = filter(movies, year >= 1990), aes(rating, gross, color = genre)) +
  geom_point() + 
  theme_bw() +
  ggtitle("The Realtionship Between Rating and Gross from 1990")

#the runtime distribution
ggplot(data = subset(movies, !is.na(certificate)) %>% filter(year >= 2000), aes(runtime, fill = certificate)) +
  geom_histogram(binwidth = 1) +
  theme_bw() +
  ggtitle("The Distribution of Runtime")

#the number of movies released from 1990
ggplot(movies %>% filter(year >= 1990), aes(year, fill = genre)) + 
  geom_bar() +
  theme_bw() +
  ggtitle("The Number of Movies Released from 1990")

#the distribution of metascore from 2000
ggplot(movies %>% filter(year >= 2000), aes(metascore, fill = genre)) + 
  geom_histogram(binwidth = 1) +
  theme_bw() +
  ggtitle("The Distribution of Metasocre from 2000")
```

# Analysis

I bulit a random forest to predcit the gross.

```{r}
#movies <- read.csv(file = "/Users/xingyang/Desktop/5020/movies.csv")
h2o.init(nthreads = -1)
rfmovies <- movies %>%
  select(-name, -director, -star1, -star2, -intro) %>%
  filter(year >= 1990) 
rfmovies$year = as.factor(rfmovies$year)
rfmovies$certificate = as.factor(rfmovies$certificate)
rfmovies$genre = as.factor(rfmovies$genre)

set.seed(1)
indxTrain <- createDataPartition(y = rfmovies$gross, p = 0.7,list = FALSE)
train <- rfmovies[indxTrain,]
test <- rfmovies[-indxTrain,]
training <- as.h2o(train)
testing <- as.h2o(test)

x <- names(rfmovies)[-6]
y <- "gross"
rf <- h2o.randomForest(x = x,
                       y = y, 
                       model_id = "rf_features",
                       training_frame = training,
                       ntrees = 300,
                       seed = 1)
rf_pred <- h2o.predict(rf, testing)
test$pred <- as.vector(rf_pred)
ggplot(test, aes(gross, pred)) +
  geom_smooth(method = "gam", se = F, col = "red")+
  geom_point(size=0.1)+
  geom_abline(col = "blue") +
  coord_fixed()
```

From above,  I think my outcome is good to predict gross. 
